### 2016-11-27 Detector/Detector.tex
Full detector chapter and first part of H->hh corrections

The \ac{LHC} does not operate on its own, a chain of accelerators leads
the protons into the \ac{LHC}. Figure \ref{fig:lhc_schematic} shows a schematic
of the \ac{CERN} accelerator complex.
\begin{figure}[h!]
\includegraphics[width=0.8\textwidth]{./Detector/Plots/LHC_default.jpg}
\caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
\label{fig:lhc_schematic}
\end{figure}
Protons originate from hydrogen gas, where electrons are stripped off the 
hydrogen atoms using an electric field. The protons then pass through an injector
chain which increases the energy of the protons in several steps. After the protons
are created from the hydrogen gas, they are accelerated to a centre of mass energy of
50 MeV in the Linac2 linear accelerator. They are then passed on to the
\acf{PSB} which accelerates the protons until they reach a centre of mass energy of 1.4 GeV.
The next accelerator in the chain, the \acf{PS}, further accelerates the protons to 25 GeV,
with the \acf{SPS} bringing the energy up to 450 GeV. When this energy has been 
reached the protons are injected into the \ac{LHC}, where they are further accelerated to 
the required centre of mass energy. The beams collide at four points
around the ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
CMS\cite{cms-jinst}, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.

@@

In order to be able to study these relatively rare processes, 
the LHC operates at high instantaneous luminosity, defined as in equation
\ref{eqn:CMSLHC_luminosity}. 
\begin{equation}\label{eqn:CMSLHC_luminosity}
\mathcal{L} = \frac{N_b^2n_bf_{\text{rev}}\gamma}{4\pi\epsilon_n\beta^{*}}F
\end{equation}

@@

Due to the high operating luminosity, multiple proton-proton collisions per 
bunch crossing are likely to occur. The average number of interactions
per bunch crossing is X in 2012, Y in 2015, Z in 2016. Additional 
interactions on top of events of interest are referred to as pile-up.

@@

Despite being further away from the interaction
point than the tracker, the materials in other parts of the detector
still need to be radiation hard. In order to be able to place
the calorimeters inside the bore of the solenoid, a compact \ac{ECAL}
had to be constructed, and to provide excellent resolution a 
highly granular system had to be designed. The lead tungstate crystals have a 
radiation length of 0.89 cm, a Moli\'ere radius of 2.2 cm, and 80\% of the light
from the crystals is emitted in 25 ns. This short radiation
length, small Moli\'ere radius and short scintillation decay time combined
with the radiation hardness of the material motivate the choice of lead tungstate.

@@

\begin{equation}\label{eqn:ecalres}
\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\bigoplus\frac{N}{E}\bigoplusC},
\end{equation}

@@

The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
plates with tiles of plastic scintillator as the active material. The tiles 
are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
beyond this range.
The light from each tile is collected with a wavelength-shifting fibre, 
which is eventually read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
sufficient to identify for example late-starting showers. The \ac{HO}, sitting
outside of the magnet and using the coil as an additional absorber, extends the 
thickness to at least 11.8 interaction lenghts. 
The active material again consists of plastic scintillator tiles which roughly
map the granularity of the tiles in the \ac{HB}, read out by feeding the light
to a hybrid photodiode via wavelength shifting fibres.
%WTF: wavelength-shifting fibres

>>>>

The \ac{LHC} does not operate on its own, a chain of accelerators leads
the protons into the \ac{LHC}. Figure \ref{fig:lhc_schematic} shows a schematic
of the \ac{CERN} accelerator complex.
\begin{figure}[h!]
\includegraphics[width=0.8\textwidth]{./Detector/Plots/LHC_default.jpg}
\caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
\label{fig:lhc_schematic}
\end{figure}
Protons originate from hydrogen gas, where electrons are stripped off the 
hydrogen atoms using an electric field. The protons then pass through an injector
chain which increases the energy of the protons in several steps. After the protons
are created from the hydrogen gas, they are accelerated to a centre of mass energy of
50 MeV in the Linac2 linear accelerator. They are then passed on to the
\acf{PSB} which accelerates the protons until they reach a centre of mass energy of 1.4 GeV.
The next accelerator in the chain, the \acf{PS}, further accelerates the protons to 25 GeV,
with the \acf{SPS} bringing the energy up to 450 GeV. When this energy has been 
reached the protons are injected into the \ac{LHC} in two counter-rotating
beams. In the \ac{LHC} ring the beams are further accelerated to the required centre of mass energy
by eight \ac{RF} cavities. At design operation the beams consist of 2808 proton bunches each made up 
of $\mathcal{O}(10^11)$ protons, spaced 25ns apart. The beams are kept in circulation
using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
a temperature of 1.9K and generating magnetic fields upwards of 8 T.
The beams collide at four points
around the \ac{LHC} ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
CMS%\cite{cms-jinst} guess we've cited this already
, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.

@@

In order to be able to study these relatively rare processes, 
the LHC operates at high instantaneous luminosity, defined as
\ref{eqn:CMSLHC_luminosity}. 
\begin{equation}\label{eqn:CMSLHC_luminosity}
\mathcal{L} = \frac{N_b^2n_bf_{\text{rev}}\gamma}{4\pi\epsilon_n\beta^{*}}F.
\end{equation}

@@

Due to the high operating luminosity, multiple proton-proton collisions per 
bunch crossing are likely to occur. The average number of interactions
per bunch crossing was 21 in 2012\cite{cms-lumi-public}. The average number of
interactions per bunch crossing lowered again at the start of Run 2, with
an average of 14 interactions per bunch crossing for the data collected
during 2015. In the data-taking period up to August 2016 the average number of interactions
per bunch crossing increased to 24\footnote{NoteToBeRemovedBeforeSubmission: Lumi pog letting us down 
here, no references for what number to quote/no prescriptions for how to calculate it. Use of theoretical
min bias cross section (80mb) vs min bias cross section tuned for pu reweighting (less than 70 mb both for
2015 and 2016) can shift the average by 5 evts or more! The 2016 number uses the theoretical
cross section (only reference to this are various sets of slides presented at conferences), 2015
number based on the min bias cross section used for pu reweighting (iirc). Assuming the 2012 numer,
for which there is a public figure, uses the theoretical mb cross section should probably re-calculate the
number for 2015.}. Additional 
interactions on top of events of interest are referred to as pile-up.

@@

Despite being further away from the interaction
point than the tracker, the materials in other parts of the detector
still need to be radiation hard. In order to be able to place
the calorimeters inside the bore of the solenoid, a compact \ac{ECAL}
had to be constructed, and to provide excellent resolution a 
highly granular system had to be designed. The lead tungstate crystals have a 
radiation length of 0.89 cm, a Moli\`ere radius of 2.2 cm, and 80\% of the light
from the crystals is emitted in 25 ns. This short radiation
length, small Moli\`ere radius and short scintillation decay time combined
with the radiation hardness of the material motivate the choice of lead tungstate.

@@

\begin{equation}\label{eqn:ecalres}
\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\bigoplus\frac{N}{E}\bigoplus C,
\end{equation}

@@

The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
plates with tiles of plastic scintillator as the active material. The brass used as 
absorber fits the constraints imposed by the environment due to its short interaction length
of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
beyond this range. 
The light from each tile is collected with a wavelength-shifting fibre, 
which is eventually read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
sufficient to identify for example late-starting showers. The \ac{HO}, sitting
outside of the magnet and using the coil as an additional absorber, extends the 
thickness to at least 11.8 interaction lenghts. 
The active material again consists of plastic scintillator tiles which roughly
map the granularity of the tiles in the \ac{HB}, read out by feeding the light
to a hybrid photodiode via wavelength shifting fibres.
%WTF: wavelength-shifting fibres
